### 2017-12-07 Docs/Thesis/docs/chapter2.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Traffic generator tools}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Network Traffic Modeling and Realistic Traffic Generation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Validation of Traffic Generator Tools}
% techniques

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Traffic generator tools}\label{sec:traffic-gen}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Network Traffic Modeling and Realistic Traffic Generation}\label{sec:modeling-traffic}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Validation of Traffic Generator Tools}~\ref{sec:validation-traffic-gen}
% techniques

@@

\section{Conclusions}

In this chapter, we review and discussed some fundamental concepts of our research: network traffic generators, network traffic modeling, and network traffic generators validation. In the section ~\ref{sec:traffic-gen} we surveyed types of traffic generators, and a comparison between its considerable variability of features. It helped us to summarize and have a deep understanding of what is available today for use, and define its gaps. Also, it helped us to see find what tools and frameworks are possible for us to use. In the section ~\ref{sec:modeling-traffic} create a brief overview putting together efforts on network traffic modeling and realistic traffic generation. On modeling, we made a short historical summary of some critical points, and on realistic traffic generation, we discussed some reference tools. Finally, we revied methodologies for validation of traffic generator tools, presenting some study cases at the end. This survey worked as a reference for the definition of our methodology of evaluation.
